Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2014-12-15 content/impl.tex

Recall that in the equivalence transformation lattice $L^\equiv$, $\bot$ means reachable
and $\top$ means unreachable.
Therefore, a result $\rho=\resultIDE(\transEq(P))$ of the equivalence IDE analysis
is converted to an IFDS result as follows:
\begin{equation}\label{eq:transEqDef}
  \backEq(\rho) = \lambda n.\{d\mid\rho(n)(d)\ne\top\}.
\end{equation}

In the correlated-calls transformation lattice $\lcc$, a map that maps any receiver
to the empty set of possible types means that the corresponding data flow path is
infeasible. Therefore, a result $\rho=\resultIDE(\transCC S(P))$ of the correlated-calls IDE analysis is
converted to an IFDS result as follows:
\begin{equation}\label{eq:transCcDef}
  \backCC(\rho) = \lambda n.\{d\mid\forall r\in S\,.\,\rho(n)(d)\neq\top_T\}.
\end{equation}

>>>>

Recall that in the equivalence transformation lattice $L^\equiv$, $\bot$ means reachable
and $\top$ means unreachable.
Therefore, a result $\rho=\resultIDE(\transEq(P))$ of the equivalence IDE analysis
is converted to an IFDS result as follows:
\begin{equation}\label{eq:transEqDef}
  \backEq(\rho) = \lambda n.\{d\mid\rho(n)(d)\ne\top\}.
\end{equation}\mtodo{Another change was that Ondrej defined $\backEq$ as $\lambda n.\{d\mid\rho(n)(d)=\top\}$
and that he defined $\backEq$ related to the equivalence transformation.}

In the correlated-calls transformation lattice $\lcc$, a map that maps any receiver
to the empty set of possible types means that the corresponding data flow path is
infeasible. Therefore, a result $\rho=\resultIDE(\transCC _S(P))$ of the correlated-calls IDE analysis is
converted to an IFDS result as follows:
\begin{equation}\label{eq:transCcDef}
  \backCC(\rho) = \lambda n.\{d\mid\forall r\in S\,.\,\rho(n)(d)\neq\top_T\}.
\end{equation}
